### 2017-03-29 thesis/discussion/discussion.tex
added some pathway stuff into section 5.1.4 - tmp commit

Finally, pathway enrichment analysis was carried out in the \gls{icgc} data sets to investigate whether there were any pathways that significantly associated with obesity (\cref{sec:pathways_enriched_in_icgc_data_sets}).
There were no pathways enriched in any of the \gls{icgc} data sets, nor the combined \gls{icgc} data set.
Although there was no significantly enriched  pathway in the \gls{icgc} data sets, it was evident from the obesity metagenes from the CR and FM data sets that the obesity metagenes were associated with the gene expressions of the obesity associated genetic signatures.
This suggested that the metagenes were able to identify some sort of genetic pattern in the data, even though these metagenes were not significantly associated with obesity.

>>>>

Finally, pathway enrichment analysis was carried out in the \gls{icgc} data sets (first with each cancer type separately, then all cancer types combined) to investigate whether there were any pathways that significantly associated with obesity (\cref{sec:pathways_enriched_in_icgc_data_sets}).
There were not many pathways identified from the \gls{kegg} and the Reactome pathway databases that were significantly enriched in the \gls{icgc} cancer data sets.
There was a substantial number of \gls{go} terms that were significantly enriched in the \gls{icgc} data, but there was no pathways that were common across all cancer types.
One thing noted from these results was that all three databases (\gls{go}, \gls{kegg} and Reactome) identified ``ABC transport'' pathway as significantly enriched in the \gls{cesc} data set.
This suggests that the ``ABC transport'' pathway may have an important role in \gls{cesc} tumour development in obese patients.
There was no significantly enriched pathway that was associated with obesity in the combined \gls{icgc} data sets.

Although there was no common pathway that associated with obesity in the \gls{icgc} data sets, it was evident from the CR and FM obesity metagenes that the obesity metagenes were associated with the gene expressions of the obesity signatures.
This suggested that the metagenes were able to identify some sort of genetic pattern in the data, even though these metagenes were not significantly associated with obesity.
